% Chapter 1

\chapter{INTRODUCTION} % Write in your own chapter title All Chapter headings in CAPS
\section{General Overview} % All Section headings in Title Case
Road accidents constitute the major part of the accident deaths all over the world. According to the Insurance Institute for Highway Safety (IIHS), new cars and its high-tech safety features have helped to lessen auto related deaths over the past 12 years. Though it credits technology for lessening auto accidents, yet the IIHS cannot help accusing bad driving behavior like drunken driving, speeding and not using seatbelts for still causing major traffic deaths. Automatic vehicle accident detection and report system is an embedded intelligence implanted into the auto- mobile. This project proposes a distributed system which alerts on the occurrence of an accident.

The purpose of the project is to find the vehicle where it is and locate the vehicle by means of sending a message using a system which is placed inside the vehicle. To help the injured first we need to know where the accident happened through location tracking and sending a message to your related one or to the emergency services. Here we use GPS and GSM modules which help to trace the vehicle. The exact location of the vehicle is sent to our remote server using the GSM shield. The assumption is that the micro controller unit (MCU) along with the GPS module is annexed onto to the air bag electronic control unit which is used as a trigger signal to detect the collision. Upon impact, the MCU notifies the emergency services about the accident and also stores this data onto the remote server along with the coordinates obtained from the GPS module, creating a digital record of the incident tagged along with date, time and location. These records could aid the government to flag accident-prone zones thereby assisting them in taking effective precautionary measures. 


